PANCHANGE_data_preprocessing

### 2020-07-20 PANCHANGE_data_preprocessing2020-07-15.Rmd
Changing yaml date to system date to reflect latest update, rather than date the script was created

---
title: "PANCHANGE_data_preprocessing"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: "03/07/2020"
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

>>>>

---
title: "PANCHANGE_data_preprocessing"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show
